General constraints on magic state protocols from the statistical mechanics of \\Wigner negativity

### 2021-06-09 magic_paper.tex

\ddd{[Title of Gour2020 paper is incorrect in the bibliography]}

@@

Our analysis applies majorization to magic states at the level of the associated Wigner distributions. However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions~\cite{arvidsson_2020, halpern_2018}.

@@

	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
	\begin{equation}
		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution. 
\end{theorem}
For magic protocols that generate unital maps the above bound reduces to the simpler form
\begin{equation}
	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
For any $\epsilon$ the upper bound can be numerically minimized over $\alpha$.
\begin{figure}[t!]
    \centering
    \subfigure[][]{%
    \label{fig:Ra}%
    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
    \subfigure[][]{%
    \label{fig:RaDiff}%
    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
    \nick{Can compare thauma and mana for other magic states now more easily}}
    \label{fig:rate_a_contour}
\end{figure}

>>>>

\nick{REFs not already cited and that I think are relevant:}
\begin{enumerate}
	\item ``Excluding joint probabilities from quantum theory''~\cite{Allahverdyan_2018}
	\item ``Quantum computation with realistic magic-state factories''~\cite{Ogorman_2017}
	\item ``Magic-State Distillation in All Prime Dimensions Using Quantum Reed-Muller Codes''~\cite{CampbellAnwar_2012}
	\item ``Resource optimized quantum architectures for surface code implementations of magic-state distillation''~\cite{holmes_resource_2019}
	\item ``Quantum advantage in postselected metrology''~\cite{arvidsson_2020}
	\item ``Quasiprobability behind the out-of-time-ordered correlator''~\cite{halpern_2018}
	\item ``Quantum Fluctuation Theorems, Contextuality, and Work Quasiprobabilities''~\cite{Lostaglio_2018}
	\item ``Quasiprobability Distribution for Heat Fluctuations in the Quantum Regime''~\cite{Levy_2020}
	\item ``A One-Way Quantum Computer''~\cite{cit:raussendorf}
	\item ``Measurement-based quantum computation on cluster states''~\cite{Raussendorf_2013}
	\item ``Contextuality as a Resource for Models of Quantum Computation with Qubits''~\cite{Vega_2017}
	\item ``On the extremal points of the $\Lambda$-polytopes and classical simulation of quantum computation with magic states''~\cite{okay2021extremal}
\end{enumerate}

@@

Our analysis applies majorization to magic states at the level of the associated Wigner distributions. However, these are in general quasi-probability distributions, so it is important to check how majorization is computed for these cases and what differences quasi-distributions bring over genuine probability distributions \nick{CITE}.

@@

	We have the following family of upper bounds on the magic distillation rate $R := m/n$,
	\begin{equation}
		R \leq \frac{F_\alpha(W_\rho) - F_\alpha(W_\tau)}{F_\alpha(W_{\rho'}) - F_\alpha(W_{\tau'})},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and $\beta F_\alpha(W_\rho) := D_\alpha (W_\rho || W_\tau) - \log \Z$ is the $\alpha$--free energy of the Wigner distribution. 
\end{theorem}
For magic protocols that preserve unital maps, the above bound reduces to the simpler form
\begin{equation}
	R \leq \frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq \frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
The upper bound can be numerically minimized over $\alpha$, for any $\epsilon$.
\begin{figure}[t!]
    \centering
    \subfigure[][]{%
    \label{fig:Ra}%
    \includegraphics[scale=0.4]{figs/Ra_vs_a_eps.pdf}}\\
    \subfigure[][]{%
    \label{fig:RaDiff}%
    \includegraphics[scale=0.4]{figs/RaDiff_vs_a_eps.pdf}}
    \caption{$R_\alpha$ and $R_\alpha - R_{\infty}$ for the Strange state distillation for unital protocols
    \nick{Can compare thauma and mana for other magic states now more easily}}
    \label{fig:rate_a_contour}
\end{figure}
